A thesis draft

### 2018-10-29 res/sections/10-ProjectAnalysis.tex
Fix typo
Add Ironhide and Astaire description

\subsubsection{Roulette Controller}
\label{chap:prjan:sec:tech:sub:SFC:sub:roulette}
Dynamic communications between VNFs would not be possible without a thrid
component acting as a route controller. Roulette fulfulls this role, providing a
backend where the single VNF can ask the next packet hop. Indeed, routes must be
submitted by another component, that we identified as Harbor (component
description available above in
sub-section~\ref{chap:prjan:sec:tech:sub:MANO:sub:harbor}). After a NS
deployment, Roulette gets instructed with a new route describing a NS. Every NS
has a proper ID (called \verb!sfid!), and thus when the classifier checks a
packet typology, it labels that packet with the specific NS ID (for a detailed
description about the SFC header see Section~\todo{Add section/chapter/paragraph
  ref!}). Finally, thanks to this label, every VNF knows the packet's chain and
it will correctly forward the it to the next VNF.

\subsubsection{Astaire}

\subsubsection{Ironhide}

@@

\subsubsection{Docker Swarm} Introduced in ??\todo{Find Docker Swarm date of
birth}, Docker Swarm allows multiple Docker nodes to cluster together and be
seen as one logical unit. This layer completely makes the underlying
infrastructure transparent: data management, as network one, are totaly managed
by Docker. Recently, Docker-compose support has been introduced, making this
one-node tool available for clustered systems. At the end of the day, on one
hand Docker Swarm provides an easy way to set up a cluster system with all the
tools configured out-of-the-box, without the necessity to set networking
configurations or installing ad-hoc storage solutions. On the other hand,
though, it doesn't have all the personalization options that Kuberentes offers,
thus making the product less flexible. This foundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs. \todo{Add Docker Swarm}

\subsubsection{Docker-compose} As briefly discussed above, Docker-compose is a tool
that allows services orchestration. It automates most of the tasks that should
be performed by hand when launching one or multiple docker containers. It's
particulary useful when more continers have to interact together,
because\todo{Write down docker-compose functionalities and describe the product
  a little bit} all the services rules are described in a simple YAML file. With
the birth of Docker Swarm, work has started to port this tool to the Swarm
framework. At the time of this writing, the procedure to port a Docker-compose
configuration in Docker Swarm is still not completely transparent, and it
requires a sort of compilation, where Docker-compose bundles all the necessaries
resources into a binary file that Docker Swarm will use to allocate the
necessary resources.

@@

\subsubsection{Openvswitch} \todo{Talk about Openvswitch!!}
\subsubsection{Openbaton}
\label{chap:prjan:sec:tech:sub:other:sub:openbaton}
Patrocined by the Institute Fraunhofer, it's a open-source, customizable NFV 
MANO-compliant framework, that offers manyconfigurations options, and since it's 
written in Java, there is the possibility to add components (plug-ins) 
dynamically. Openbaton can be installed as a normal computer program (they 
offer packages for the most common distros) but it can be deployed on Docker 
containers too. It's designed to work with cloud providers like Amazon or 
Google Compute engine, but it offers compability with on-permise cloud 
solutions like Openstack, where it deploys virtual machines using the API
the platform offers. It can store VNF configurations saved as TOSCA
YAML\todo{What does TOSCA mean? Find out} and it can handle multiple
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecyle management
out-of-the-box, with the possibility to customize it based on the user needs.
Its modular design allows developers to change parts of the codebase with custom
ones, making the product really flexible to different platforms. Performing this
operation requires a deep knowlege of the framework though.
\begin{figure}[h]
 \centering \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}
% \paragraph{SDN?}

>>>>

\subsubsection{Roulette Controller}
\label{chap:prjan:sec:tech:sub:SFC:sub:roulette}
Dynamic communications between VNFs would not be possible without a thrid
component acting as a route controller. Roulette fulfills this role, providing a
backend where the single VNF can ask the next packet hop. Indeed, routes must be
submitted by another component, that we identified as Harbor (component
description available above in
sub-section~\ref{chap:prjan:sec:tech:sub:MANO:sub:harbor}). After a NS
deployment, Roulette gets instructed with a new route describing a NS. Every NS
has a proper ID (called \verb!sfid!), and thus when the classifier checks a
packet typology, it labels that packet with the specific NS ID (for a detailed
description about the SFC header see Section~\todo{Add section/chapter/paragraph
  ref!}). Finally, thanks to this label, every VNF knows the packet's chain and
it will correctly forward the it to the next VNF.

\subsubsection{Astaire}
As is possible to denote, a VNF doesn't only process the incoming packets, 
but it has to manage the communications and the related forward operations. To 
possibly ease part of the transmission problem and to make it easier to create a 
VNF without requiring the whole knowledge about SFC, it has been decided to 
build a framework, Astaire, that could keep the SFC related details decoupled 
from the core of the VNF, in other words, the entity that actually elaborates 
the packet. Built using an event-based pattern, it presents hooks that allow 
other software written in different languages from the Astaire one (e.g. Java), 
to be called dynamically at runtime in order to process the packet. The result 
of this elaboration gets returned to astaire, that performs the beforehand 
cited operations of VNFs communications and forwarding.

\subsubsection{Ironhide}
As described in chapter~\ref{chap:archimpl}, the whole framework need to have 
and entry and an exit point. These, defined as \textit{Ingress} and 
\textit{Egress} points, are performed by Ironhide. Ironhide acts like a proxy, 
hiding the whole packet processing to the sender $S$ and the receiver $R$. When 
a client $S$ performs a request to $R$, the packet actually goes through 
Ironhide, who has an internal classifier that it is able to recognise the type 
of connection and to choose the right NS the packet has to go through. This 
process in foundamental since it keeps the connection between $S$ and $R$ up, 
for both TCP and UDP based communications.

@@

\subsubsection{Docker-compose} 
Docker-compose is a tool that allows services orchestration. It automates most 
of the tasks that should be performed by hand when launching one or multiple 
docker containers. It's particulary useful when more continers have to interact 
together, because\todo{Write down docker-compose functionalities and describe 
the product a little bit} all the services rules are described in a simple 
YAML file. With the birth of Docker Swarm, work has started to port this tool to 
the Swarm framework. At the time of this writing, the procedure to port a 
Docker-compose configuration in Docker Swarm (which a description of the 
product can be found in 
sub-section~\ref{chap:prjan:sec:tech:sub:other:sub:swarm}) is still not 
completely transparent, and it requires a sort of compilation, where 
Docker-compose bundles all the necessaries resources into a binary file that 
Docker Swarm will use to allocate the necessary resources.

@@

\subsubsection{Docker Swarm}
\label{chap:prjan:sec:tech:sub:other:sub:swarm}
Introduced in ??\todo{Find Docker Swarm date of birth}, Docker Swarm allows 
multiple Docker nodes to cluster together and be seen as one logical unit. This 
layer completely makes the underlying infrastructure transparent: data 
management, as network one, are totaly managed by Docker. Recently, 
Docker-compose support has been introduced, making this one-node tool available 
for clustered systems. At the end of the day, on one hand Docker Swarm provides 
an easy way to set up a cluster system with all the tools configured 
out-of-the-box, without the necessity to set networking configurations or 
installing ad-hoc storage solutions. On the other hand, though, it doesn't have 
all the personalization options that Kuberentes offers, thus making the product 
less flexible. This foundamental characteristic, although, makes the two 
solutions have different use cases leading to different market needs.

\subsubsection{Openvswitch} \todo{Talk about Openvswitch!!}
\subsubsection{Openbaton}
\label{chap:prjan:sec:tech:sub:other:sub:openbaton}
Patrocined by the Institute Fraunhofer, it's a open-source, customizable NFV 
MANO-compliant framework, that offers manyconfigurations options, and since 
it's 
written in Java, there is the possibility to add components (plug-ins) 
dynamically. Openbaton can be installed as a normal computer program (they 
offer packages for the most common distros) but it can be deployed on Docker 
containers too. It's designed to work with cloud providers like Amazon or 
Google Compute engine, but it offers compability with on-permise cloud 
solutions like Openstack, where it deploys virtual machines using the API
the platform offers. It can store VNF configurations saved as TOSCA
YAML\todo{What does TOSCA mean? Find out} and it can handle multiple
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecyle management
out-of-the-box, with the possibility to customize it based on the user needs.
Its modular design allows developers to change parts of the codebase with custom
ones, making the product really flexible to different platforms. Performing this
operation requires a deep knowledge of the framework though.
\begin{figure}[h]
 \centering \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}
